---
title: "Project of Module 5"
author: "Dario Godoy"
date: "2024-07-01"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## In this project

This project corresponds to Module 5 of Developing Data Products Course. This assignment has two parts:
   
1. Create a Shiny app and deploy it. 
2. Prepare a reproducible pitch presentation about the app.

The app include:
   
1. Two numeric input boxes
2. A prediction model on dataset
3. An output of concentration predicted on inputs with the calculated model

## Use of app

The origin of data is "Pharmacokinetics of Theophylline dataset" ("Theoph"). The Theoph data frame has 132 rows and 5 columns of data from an experiment on the pharmacokinetics of theophylline. The variables are:   

* **Subject**: an ordered factor with levels 1, ..., 12 identifying the subject on whom the observation was made. The ordering is by increasing maximum concentration of theophylline observed.   

* **Wt**: weight of the subject (kg).   

* **Dose**: dose of theophylline administered orally to the subject (mg/kg).  

* **Time**: time since drug administration when the sample was drawn (hr).   

* **conc**: theophylline concentration in the sample (mg/L).   


Additional data are in my GitHub Repository.

## Theof dataset

Boeckmann, Sheiner and Beal (1994) report data from a study by Dr. Robert Upton of the kinetics of the anti-asthmatic drug theophylline. Twelve subjects were given oral doses of theophylline then serum concentrations were measured at 11 time points over the next 25 hours.

```{r}
str(Theoph)

```

## Plot Theoph dataset

```{r, echo=FALSE,fig.align='center'}
plot(conc~Time, data = Theoph, col = Subject,
     main = "Theophylline concentration vs. Time", 
     xlab = "Time(h)", ylab = "conc(mg/L)", pch = 16)
```
